SDG contributions

### 2023-09-15 article/article.qmd
add label to figure
the figure is not only about SDG 2

```{r}
# look at relative specialisation to identify how global south is represented in
# SDG 2

continent_specialisation <- normalised_region_share_time %>% 
  rename(nn_sdg = nn, share_sdg = share) %>% 
  mutate(year = as.character(year)) %>% 
  left_join(mag_2021_normalised_region_share_time) %>% 
  mutate(specialisation = share_sdg / share)
```

```{r, fig.width=10, fig.height=10}
#| fig-cap: "Specialisation of world regions. The specialisation factor is
#| calulated by dividing the share of research towards a certain SDG by the 
#| overall share of research coming from the same region. Melanesia, Polynesia
#| and Micronesia are omitted due to low cell counts."
continent_specialisation %>% 
  filter(!sub_continent %in% c("Melanesia", "Polynesia", "Micronesia")) %>% 
  ggplot(aes(as_year(year), specialisation, colour = fix_sdg(SDG_label))) +
  geom_hline(yintercept = 1, colour = "grey30") +
  geom_line() +
  geom_point(size = 1.1) +
  facet_wrap(vars(sub_continent)) +
  colorspace::scale_color_discrete_qualitative() +
  theme(legend.position = "top") +
  labs(x = NULL, colour = NULL, y = "Specialisation factor")
```

>>>>

```{r}
# look at relative specialisation to identify how global south is represented in
# various SDGs
continent_specialisation <- normalised_region_share_time %>% 
  rename(nn_sdg = nn, share_sdg = share) %>% 
  mutate(year = as.character(year)) %>% 
  left_join(mag_2021_normalised_region_share_time) %>% 
  mutate(specialisation = share_sdg / share)
```

```{r, fig.width=10, fig.height=10}
#| label: fig-specialisation-by-world-region
#| fig-cap: "Specialisation of world regions. The specialisation factor is
#| calulated by dividing the share of research towards a certain SDG by the 
#| overall share of research coming from the same region. Melanesia, Polynesia
#| and Micronesia are omitted due to low cell counts."
continent_specialisation %>% 
  filter(!sub_continent %in% c("Melanesia", "Polynesia", "Micronesia")) %>% 
  ggplot(aes(as_year(year), specialisation, colour = fix_sdg(SDG_label))) +
  geom_hline(yintercept = 1, colour = "grey30") +
  geom_line() +
  geom_point(size = 1.1) +
  facet_wrap(vars(sub_continent)) +
  colorspace::scale_color_discrete_qualitative() +
  theme(legend.position = "top") +
  labs(x = NULL, colour = NULL, y = "Specialisation factor")
```
